Use and acquisition of causal knowledge in a decision making process

### 2018-04-23 Segundo_Semestre/Seminario/Semana12/Beamer_Template.tex
adding hypothesis

\title[Short title]{Main Topic } % The short title appears at the bottom of every slide, the full title is only on the title page

@@

	\item Human beings conceive their actions upon the world as \textit{interventions} (\cite{hagmayer2009decision})

@@

		The structure of the causal graph produces some equivalence rules between observational an interventional data.
		\begin{teo}{\label{docalculus}} (\cite{pearl2009causality})\\
		Sea $\mathcal{G}$ un modelo gráfico causal y $P_{\mathcal{G}}$ la medida de probabilidad inducida por el modelo; entonces, para cualesquiera conjuntos disjuntos de variables $X,Y,Z,W$ 	se cumple que
		\item If $Y$ is conditionally independent from $Z$ given $X$ y $W$ in $\mathcal{G}_{\bar{X}}$, then
		\[ P_{\mathcal{G}}(Y=y | do(X=x), Z=z, W=w) = P_{\mathcal{G}}(Y=y | do(X=x), W=w). \]
		\item Si en el grafo $\mathcal{G}_{\bar{X}\underline{Z}}$ se cumple que $Y$ es condicionalmente independiente de $Z$ dados $X$ y $W$, entonces
		\[ P(Y=y | do(X=x), do(Z=z), W=w) = P(Y=y | do(X=x), Z = z, W=w). \]
		\item Sea $Z(W)$ el conjunto de nodos en $Z$ tales que no son ancestros de ningún nodo en $W$ en el grafo $\mathcal{G}_{\bar{X}}$. Si en el grafo $G_{\bar{X}, \bar{Z(W)}}$ se cumple que $Y$ es condicionalmente independiente de $Z$ dados $X$ y $W$ entonces,
		\[ P(Y=y | do(X=x), do(Z=z), W=w) = P(Y=y | do(X=x), W=w). \]

@@

	\subsection{Game Theory}
		\subsubsection{Games in normal form}
		\subsubsection{Games in extensive form}
\section{Research Question}
\begin{frame}
\frametitle{Research Question}
How can an intelligent agent acquire and use causal knowledge from his interaction with an uncertain environment in a decision making process?
\end{frame}

@@

\section{Previous work}
	\subsection{Causality and Decision Theory}
	\subsection{Optimal Interventions}
	\begin{frame}[allowframebreaks]
	\frametitle{Identifying Optimal Interventions}
	\begin{itemize}
		\item \cite{lattimoreNIPS2016} study the problem of decision making under uncertainty in causal models where the causal model is completely known.
		\item In their setup, the actions or choices available to dhe decision maker are interventions in the model.
		\item They look for the minimal-regret intervention that maximices some reward variable. 
		\item They show that optimal intervention can be found faster than if no causal info was considered. Open question of what to do when the causal graph is unknown
		\item Later, \cite{sen2017identifying} start with the same setting than in \cite{lattimoreNIPS2016} but they consider the case when not all of the graph is known. 
		\item They also find the optimal intervention over some variable in the unknown part of the model. They improve the results of \cite{lattimoreNIPS2016} in experiments, but they still require knowing conditional distributions.
	\end{itemize}
\end{frame}
\section{Objectives}
	\subsection{General Objective}
	\begin{frame}
	The proposed research has 2 general objectives: 
	\begin{itemize}
	\item Find the way in which an agent facing an uncertain environment (governed by a causal model) can use causal knowledge in order to make good choices and improve his performance when compared to non-causal ways of choosing.
	\item Find the way in which an agent can acquire causal information while interacting with an uncertain (governed by a causal model) environment.
	\end{itemize}
	\end{frame}
	\subsection{Specific Objectives}
	\begin{frame}[allowframebreaks]
	\frametitle{Specific Objectives}
	\begin{itemize}
\item To find a way to specify beliefs about causal structure; i.e., find (or build) a family of parametric distributions that represent in a coherent way beliefs or previous knowledge about the causal structure of some environment.
\item  We have to consider two cases: if the decision-maker (or the owner of the beliefs) knows the maximum number of variables that the causal model can have.
\item On the other side, if the agent doesn't know the max number of variables.
\item To find a way of effectively using causal knowledge that the agent has at a given moment.
\item Develop an update criterion for the beliefs of the agent based upon what he has observed from the environment while interacting. This updating must be achieved in a way that the sequence of models converges to the true model. In the Bayesian Non parametric setting this is known as \textit{consistency} (\cite{ghosal2017fundamentals}). Also, the beliefs obtained must be coherent with the decision making since we will be using those results. 
\item An aproximate soluton criteria: maybe we can't wait until convergence, so what can be done with the current knowledge.
\end{itemize}
	\end{frame}
\section{Methodology}
	\subsection{Hypothesis}
	\begin{frame}
	\frametitle{Hypothesis}
	Under certain conditions, an agent can acquire and use causal knowledge from interaction with an uncertain environment and effectively use it in a decision problem under uncertainty.
	\end{frame}
	\subsection{Working methodology}
\section{Preliminary Results}
\begin{frame}
\frametitle{Preliminary Results}

>>>>

\title[Short title]{Use and acquisition of causal knowledge in a decision making process} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

	\item Human beings conceive their actions upon the world as \textit{interventions} (\cite{hagmayer2009decision}).

@@

		The do calculus is a set of rules which allow, under certain conditions, to express interventional statements in terms of observational statements.

@@

	\subsection{Game Theory}
\begin{frame}
\frametitle{Game Theory}
Game Theory is an area of Mathematics that is used to model strategic interaction situations, which can be interpreted as multi-agent decision problems, where the outcomes for each player depend on the actions of the other players. Several classes exist:
\begin{itemize}
\item Strategic Games
\item Extensive Games
\item Stochastic Games
\end{itemize}
\end{frame}
\section{Research Question}
\begin{frame}
\frametitle{Research Question}
In an uncertain environment where the relationship between events is governed by some causal mechanism, how can an intelligent agent acquire and use causal knowledge from his interaction with the environment in a decision making proces in order to learn faster to choose good actions?
\end{frame}

	\subsection{Hypothesis}
	\begin{frame}
	\frametitle{Hypothesis}
Let $\mathcal{G}$ a causal graphical model whose probability distribution $P_\mathcal{G}$ satisfies (the axioms). Let $(D,E,c)$ a decision problem whose uncertain events are related to the variables in $\mathcal{G}$. Then, if a decision maker doesn't know the probabilities of the uncertain events in $E$, then by repeatedly making decisions he can learn causal information and use it to find the optimal actions (in the sense of expected utility theory) in less rounds than if he doesn't consider causal information.
	\end{frame}

@@

\section{Previous work}
	\subsection{Optimal Interventions}
	\begin{frame}[allowframebreaks]
	\frametitle{Identifying Optimal Interventions}
	\begin{itemize}
		\item \cite{lattimoreNIPS2016} study the problem of decision making under uncertainty in causal models where the causal model is completely known.
		\item In their setup, the actions or choices available to dhe decision maker are interventions in the model.
		\item They look for the minimal-regret intervention that maximices some reward variable. 
		\item They show that optimal intervention can be found faster than if no causal info was considered. Open question of what to do when the causal graph is unknown
		\item Later, \cite{sen2017identifying} start with the same setting than in \cite{lattimoreNIPS2016} but they consider the case when not all of the graph is known. 
		\item They also find the optimal intervention over some variable in the unknown part of the model. They improve the results of \cite{lattimoreNIPS2016} in experiments, but they still require knowing conditional distributions.
	\end{itemize}
\end{frame}

\section{Objectives}
	\subsection{General Objective}
	\begin{frame}
	The proposed research has 2 general objectives: 
	\begin{itemize}
	\item Find the way in which an agent facing an uncertain environment (governed by a causal model) can use causal knowledge in order to make good choices and improve his performance when compared to non-causal ways of choosing.
	\item Find the way in which an agent can acquire causal information while interacting with an uncertain (governed by a causal model) environment.
	\end{itemize}
	\end{frame}
	\subsection{Specific Objectives}
	\begin{frame}[allowframebreaks]
	\frametitle{Specific Objectives}
	\begin{itemize}
\item To find a way to specify beliefs about causal structure; i.e., find (or build) a family of parametric distributions that represent in a coherent way beliefs or previous knowledge about the causal structure of some environment.
\item  We have to consider two cases: if the decision-maker (or the owner of the beliefs) knows the maximum number of variables that the causal model can have.
\item On the other side, if the agent doesn't know the max number of variables.
\item To find a way of effectively using causal knowledge that the agent has at a given moment.
\item Develop an update criterion for the beliefs of the agent based upon what he has observed from the environment while interacting. This updating must be achieved in a way that the sequence of models converges to the true model. In the Bayesian Non parametric setting this is known as \textit{consistency} (\cite{ghosal2017fundamentals}). Also, the beliefs obtained must be coherent with the decision making since we will be using those results. 
\item An aproximate soluton criteria: maybe we can't wait until convergence, so what can be done with the current knowledge.
\end{itemize}
	\end{frame}
\section{Methodology}

	\subsection{Working methodology}
\section{Preliminary Results}
\begin{frame}
\frametitle{Preliminary Results}
For the preliminary results we set up a toy example (the same one that we have been using) and analyze 3 separate cases in order of growing difficulty:
\begin{itemize}
\item In the first case, the decision maker knows it all.
\item In the second case, the decision maker only knows for certain the structure of the model, but not its parameters so he has beliefs about them.
\item In the third case, the decision maker knows nothing at all, so he has general beliefs about the causal model itself.
\end{itemize}
\end{frame}
